---
title: "Go Fish V2 Explanation and Description Responses"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(patchwork)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
```



```{r globals, include=FALSE}
# Data files
SUMMARY_DATA = "01_go_fish_v2_meta.csv"
TRIAL_DATA = "02_go_fish_v2_trials.csv"
EVAL_DATA = "03_go_fish_v2_evaluation.csv"
MEMORY_DATA = "04_go_fish_v2_memory.csv"

REPEAT_SONA = c("user_1593731799971") # One participant did the experiment twice

```



```{r analysis_fxn, include=FALSE}
# Read in and process summary data file
read_summary_data = function(filepath) {
  # Read in data at filepath and add/modify columns as needed
  summary_data = read_csv(filepath)
  summary_data = summary_data %>%
    mutate(condition = ifelse(is_control == TRUE, "Describe", "Explain"),
           experiment_completion_time = (expt_end_ts - expt_start_ts) / 1000)
  return(summary_data)
}

# Read in and process data from explain/describe trials
read_trial_data = function(filepath) {
  trial_data = read_csv(filepath)
  trial_data = trial_data %>%
    mutate(
      condition = ifelse(is_control == TRUE, "Describe", "Explain"),
      input_correct = (input_prediction_catches_fish == prediction_catches_fish))
  trial_data$input_evidence_response = str_replace_all(
    trial_data$input_evidence_response, "\n" , "[newline]")
  return(trial_data)
}

# Read in and process data from rule evaluation task
read_evaluation_data = function(filepath) {
  evaluation_data = read_csv(filepath)
  evaluation_data = evaluation_data %>%
    mutate(condition = ifelse(is_control == TRUE, "Describe", "Explain"))
  return(evaluation_data)
}
```



```{r data, include=FALSE}
# Read in data
summary_data = read_summary_data(SUMMARY_DATA)
trial_data = read_trial_data(TRIAL_DATA)
evaluation_data = read_evaluation_data(EVAL_DATA)

# remove repeat user
summary_data = summary_data %>%
  filter(!subjID %in% REPEAT_SONA)
trial_data = trial_data %>%
  filter(!subjID %in% REPEAT_SONA)
evaluation_data = evaluation_data %>%
  filter(!subjID %in% REPEAT_SONA)
```



# Summary
This document is intended for easy review and analysis of participant free response data. 

We display participant explanations and descriptions during the evidence phase of the experiment. 

```{r condition_summary}

summary_data %>%
  group_by(condition) %>%
  summarize(participants = n()) %>%
  kable(col.names = c("Condition", "Participants"))

```



# Explanations

Below we list each subject's trial explanations ordered by trial index (1-8). 

TODO add their eventual evaluation of the target rule (and distractors?)


```{r explanations}

trial_data %>%
  filter(condition == "Explain") %>%
  select(subjID, condition, trial_index, input_evidence_response) %>%
  arrange(subjID, trial_index) %>%
  kable(col.names = c("Subject ID", "Condition", "Trial", "Explanation"))

```



# Descriptions

Below we list each control subject's trial descriptions ordered by trial index (1-8).

TODO add their eventual evaluation of the target rule (and distractors?)


```{r descriptions}

trial_data %>%
  filter(condition == "Describe") %>%
  select(subjID, condition, trial_index, input_evidence_response) %>%
  arrange(subjID, trial_index) %>%
  kable(col.names = c("Subject ID", "Condition", "Trial", "Description"))

```


